---
title: "BMI calculator documentation"
author: "GE"
date: "5 December 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Explanations

BMI calculator is an application that, given your weight (in lbs or kgs) and your height (in inches or meters) calculates your BMI. Body mass index (BMI) is a general measurement which attempts to quantify
the amount of tissue mass in a person and show whether they are within a healthy range for their height. 

This measurement is not supposed to replace a visit to the doctor for a regular check of your weight. 
Possible distorting factors - pregnanancy, puberty/childhood, battling cancer.

Additionally, women and men generally have different healthy ranges

## Ranges

- 15 - 18.5 - underweight
- 18.5 - 25 - normal
- 25 - 30 - overwieght
- 30 - 35 - obese class I - obese
- 35 - 40 - obese class II - severely obese
- 40 + - obese class III - very severely obese

## Formula used for calculations

```{r cars, echo = TRUE, eval = TRUE}
meters <- 1.75
kgs <- 70
BMI <- kgs/(meters^2)
print(BMI)
```

## How to use
Put in your height and weight and check the radio button with the correst type of measurement. The BMI is calculated automatically.

